Proof No Diamond (3 layers)

### 2023-10-09 Yuke No Diamond for 3 layers.tex
proofs

\begin{lemma}
	Suppose $L$ is a layer and $L'$ is the next layer, and  the lower and upper bounds for each node $n$ such that $S(n)\neq 0$ in $L$ stored by the approximation method Interval Arithmetic equal to the exact lower and upper bounds of it.

	 Then Interval Arithmetic can obtain the exact lower and upper bounds for every node $m$ such that $S(m)\neq 0$ in $L'$.
\end{lemma}

\begin{proof}
	Suppose $m$ is a node in $L'$ such that $S(m)\neq 0$. Without loss of generality, we assume $S(m)=1$, and $S(m)=-1$ will be similar. Interval Arithmetic will compute its upper bound using $m=\sum_{n}w(mn)\hat{n}+b,$ by taking all $n$ that $w(mn)>0$ to upper bound and taking all $n$ that $w(mn)<0$ to lower bound.

>>>>

The DeepPoly function for $b$ can be expressed by the following steps.
First, we partition the set of indices $i$ as $I,I_0,I^+,I^-$ with:
\begin{itemize}
	\item $i \in I$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always positive irrespective of $Y=(a_j)_j$, in which case 
	$\bar{f}(b_i^+)(Y)=\underline{f}(b_i^+)=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$, and else:
	\item $i \in I_0$ if the sign of $b_i^-=\sum_{j} w_{a_j b_i} a_j + B_{b_i}$ is always negative irrespective of $Y=(a_j)_j$, in which case $\bar{f}(b_i^+)=\underline{f}(b_i^+)=0$,	and else:
	\item $i \in I^+$ if $w_{b_i c}>0$, and:
	\item $i \in I^-$ if $w_{b_i c}<0$.
	\end{itemize}

Remark that for all $i \notin I$, we have $\underline{f_i}(b_i^+)(Y)=0$.

We have:
\begin{align*}
	\bar{f}(c)(Y) = &
	bias_c + \sum_{b \in I} w_{bc}\sum_{a} w_{a b} weight(a) + bias_{b} \\
	& + \sum_{b \in I^+} w_{b c} \cdot \bar{f}(ReLU(\sum_{a} w_{a b} weight(a) 
	+ Bias_{b}))(Y) 
	\end{align*}

We proceed inductively, and prove the inductive step.
The initialization is obvious as DeepPoly is always exact for the initialization layer.

\begin{lemma}
	Let $L,L'$ two consecutive layers.
	Assume for all node $m$ of $L$ that the lower and upper bounds for $m$ used by DeepPoly equals to the exact lower and upper bounds of $m$.

	Then DeepPoly computes the exact lower and upper bounds for every node $n$ of layer $L'$.
\end{lemma}

\begin{proof}
	Suppose $n$ is a node in $L'$ such that $S(n)\neq 0$ (otherwise, it is trivial). 
	First assume $S(n)=1$. The case $S(n)=-1$ is similar.

	Deeppoly computes its upper bound using $m=\sum_{n}w(mn)\hat{n}+b,$ by taking all $n$ that $w(mn)>0$ to upper bound and taking all $n$ that $w(mn)<0$ to lower bound.
